### 2018-07-20 Manuscripts/cog-psych/revision/methods_results_e3.tex
major update. many things. to ken/xian

\sxlnote{I felt like there could be a little more explanation in terms of
  justifying this experiment so I added an extra sentence (the second last in
  the following paragraph) - I don't have too strong feelings about it so please
  feel free to remove if you think it's too much. Also see the footnote
  addressing the paper's lack of category learning fits. It's a bit of a cop
  out, but entirely true!}

Although category generation is an intriguing aspect of human cognition, it has
played a relatively limited role in the broader categorization literature. To
establish that contrast plays a broader role in categorization, we conducted a
traditional category learning study. In it, participants learned two categories,
where the categories learned by each participant in Experiment 3 was yoked to
the Alpha shown and Beta generated by each participant in Experiment 2. Our goal
is to investigate whether model performance (in generating categories) is
consistent with human performance (in learning those categories).\footnote{It is
  possible to adjust the present models of category generation such that they
  can make category learning predictions. However, such an adjustment makes the
  strong assumption that the very same processes governing category generation
  also apply to category learning. Taking this approach would fall outside the
  scope of the current investigation.} Specifically, if contrast plays a
broader role in categorization, then Beta categories rated as "better" according
to the contrast models should be easier for participants to learn.

\subsection{Participants, Materials, and Procedure}

@@

Overall accuracy of the participants was high, with a mean error rate of $.19$
($SD = .19$). Error rates for each block are presented in Figure
\ref{fig:learningcurve}.

@@

The greatest correlations were observed when fitting with the contrast models.
Specifically, PACKER correlated with human performance with
$r = .65, 95\% CI$\footnote{Confidence intervals were obtained using a bootstrap
  method with 1000 bootstrap samples.}$ [.47,.78]$, and the representativeness
model correlated with human performance with $r = .56, 95\% CI [.38, .72]$.
Copy-and-tweak yielded a correlation of $r = .45, 95\% CI [.29, .61]$ and the
hierarchical Bayesian model yielded a similar correlation of
$r = .46, 95\% CI [.30, .61]$. These results are graphically presented in Figure
\ref{fig:perror_corr}.

>>>>

Although category generation is an intriguing aspect of human cognition, it has
played a relatively limited role in the broader categorization literature. To
establish that contrast plays a broader role in categorization, we conducted a
traditional category learning study. In it, participants learned two categories,
where the categories learned by each participant in Experiment 3 was yoked to
the Alpha shown and Beta generated by each participant in Experiment 2. Our goal
is to investigate whether model performance (in generating categories) is
consistent with human performance (in learning those categories). Specifically, if contrast plays a broader role in categorization, then Beta categories rated as "better" according
to the contrast models should be easier for participants to learn.
%\footnote{It is possible to adjust the present models of category generation such that they can make category learning predictions. However, such an adjustment makes the strong assumption that the very same processes governing category generation also apply to category learning. Taking this approach would fall outside the scope of the current investigation.} 
\subsection{Participants, Materials, and Procedure}

@@

Overall accuracy of the participants was high, with a mean error rate of $.19$
($SD = .19$). Aggregated error rates for each block are presented in Figure
\ref{fig:learningcurve}.

@@

The greatest correlations were observed when fitting with the contrast models.
Specifically, PACKER correlated with human performance with
$r = .65, \ 95\% CI$\footnote{Confidence intervals were obtained using a bootstrap
  method with 1000 bootstrap samples.}$ \ [.47,.78]$, and the representativeness
model correlated with human performance with $r = .56, \ 95\%  CI \ [.38, .72]$.
Copy-and-tweak yielded a correlation of $r = .45, 95\% CI \ [.29, .61]$ and the
hierarchical Bayesian model yielded a similar correlation of
$r = .46, 95\% CI \ [.30, .61]$. These results are graphically presented in Figure
\ref{fig:perror_corr}.
